Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-20 PaperBCJ.tex
Corrections
Corrections

Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above. For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS were used for acquire images and test the classification performace of the CNN.
\\

@@

Samples were obtained from images captured in different maize fields. Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and for provide to Net of reliable samples which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD). Maize at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant. This was achieved by monitoring the obtained samples through an external display. Examples of the images captured are shown below.

@@

One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed were considered, obtained in different maize crops that the training dataset. For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image were obtained with the chosen hardware, we started the classification in Caffe without modifications in Software. The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\

\begin{table}[h!]
\centering
\begin{tabular}{|p{1.1cm}|p{1.9cm}|p{1.95cm}|p{2cm}|} 
 \hline
 \multicolumn{4}{ |c| }{\textbf{GPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 951 $\mu$s \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
 \hline 
 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
 \hline
\end{tabular}
\caption{Test with the three types of Hardware}
\label{table:4}
\end{table}

@@

The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document Batching were used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software. For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\

@@

The results shown that classification time by GPU get worse by 66\%, mainly due OpenBLAS make extense use of CPU Threads causing that not all the parameters of the net were computed by GPU like

@@

-Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 99\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases. \\

In this paper  we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes of 44580 segmented images. \\

@@

In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net. \\

>>>>

Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above. For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS was used for acquire images and test the classification performace of the CNN.
\\

@@

Samples were obtained from images captured in different maize fields. Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and for provide to Net of reliable samples which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD). Maize Plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant. This was achieved by monitoring the obtained samples through an external display. Examples of the images captured are shown below.

@@

One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

For this stage, another dataset with 202 images of maize plants in stage V3-V7 and 202 images of weed were considered, obtained in different maize crops that the training dataset. For this test and in order to have a reliable value its considered to classify ten times the dataset, so the average time of classification by image was obtained with the chosen hardware, we started the classification in Caffe without modifications in Software. The results were comparated between cNET with 64 and 16 filters and there are shown in the next Table \ref{table:4}.\\

\begin{table}[h!]
\centering
\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
 \hline
 \multicolumn{4}{ |c| }{\textbf{GPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 951 $\mu$s \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
 \hline 
 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
 \hline
\end{tabular}
\caption{Test with the three types of Hardware}
\label{table:4}
\end{table}

@@

The results shown previously are not definitive because Caffe has ways to optimize the classification of datasets of images, for this document batching was used to classify the dataset of each class in a single forward pass and the use of Multithreading by OpenBLAS math software. For each hardware, Caffe were recompiled with OpenBLAS instead of Atlas, in the program all images  were entered in a vector to be classified in an only batch per each class, also OpenBLAS was configured to use the 4 cores of each hardware to obtain fair results, the obtained results are the following \\

@@

The results show that for the GPU Classification time it has worsened by 66 \%, mainly because the OpenBLAS Library makes extensive use of the CPU threads causing that not all parameters will be computed by GPU as in the previous test. Instead, when the CPU is used the results are better, because the operations are executed using each of the four cores, in the case of the CPU we notice a 22 \% and for 6.3 \% for the Raspberry Pi \\

@@

-Este paper estudia una red neuronal convolucional para la clasificacion entre maiz y mala hierba, para lo cual se utilizo algunas arquitecturas de red, de donde la que proporciono mejores resultados fue la Cnet, con un 97.26\% de presicion en el entrenamiento al usar un datasetc de 44580 imagenes conteniendo las dos clases. \\

In this paper  we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 97.23 \% of accuracy of training, using a dataset of both classes of 44580 segmented images. \\

@@

In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuracy of the net, it value increased 1 \% in comparation with the original net. \\
